Observed vs. Simulated Year Comparison

### 2022-01-05 03-post-process/compare-sim-to-obs.Rmd
Fix typos in compare sim to obs

---
title: "Observed vs. Simulated Year Comparison"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`"
output: html_document
params:
  scenario:
    label: "Scenario"
    value: "base-with-sim-medium"
    input: text
editor_options: 
  chunk_output_type: console
---

@@

# extract the two key structures from this object
# post = model_info$post                               # full posterior takes a long time to run on this script
post = post_thin(model_info$post, keep_percent = 0.05)  # uncomment this to run document with 10% of the retained MCMC samples
jags_data = model_info$jags_data
```

@@

# for each posterior sample, calculate the total aggregate return
out_nor = out_hor = NULL
for (i in 1:nrow(Ma)) {
  Ma_i = array_format(Ma[i,])
  nor = Ma_i[,1,1,] + Ra_i[,2,1,]
  hor = Ra_i[,2,2,]

>>>>

---
title: "Observed vs. Simulated Year Comparison"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`"
output: html_document
params:
  scenario:
    label: "Scenario"
    value: "new-BH"
    input: text
editor_options: 
  chunk_output_type: console
---

@@

# extract the two key structures from this object
# post = model_info$post                               # full posterior takes a long time to run on this script
post = post_thin(model_info$post, keep_percent = 0.05)  # uncomment this to run document with 5% of the retained MCMC samples
jags_data = model_info$jags_data
```

@@

# for each posterior sample, calculate the total aggregate return
out_nor = out_hor = NULL
for (i in 1:nrow(Ma)) {
  Ma_i = array_format(Ma[i,])
  nor = Ma_i[,1,1,] + Ma_i[,2,1,]
  hor = Ma_i[,2,2,]
